Temporal Graph Cube

### 2023-01-05 revision/response.tex

\begin{Comments}
Authors provide similarity of snapshots and two ratios in the Sec. 5. All of them are calculated based on the edges’ number. Why do you use similarity but not two ratios to proof the effectiveness?
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
In the experiments, authors should add an experiment of comparison with existing methods to evaluate the efficiency of their model.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The study of related works is insufficient, and some of the results and limitations of existing works are not discussed.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The second parameter of MergeSnapshotExtre on Line 11, Algorithm 5 should be (u’, v’, t, a)?
\end{Comments}
\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $. In line 11 of Algorithm 5, the algorithm inserts $ e' $ into $ treeNode.snapshot $, which is equivalent to merge two snapshots: $ treeNode.snapshot $ and a temporary snapshot consisting of only $ e' $. However, edges in snapshot of each tree node are in form of $ (u,v,max,min) $, so we need to transform $ e' $ into $ (u',v',a,a) $, since $ a $ is both the maximum and minimum value of the numeric attribute in $ e' $. $ t $ is only used to determine whether the left child or the right child of $ treeNode $ should also be updated.

### 2023-01-06 revision/response.tex

The point-to-point responses are given below.

\section{Response to Reviewer \#1}
\begin{Comments}
The expression of motivation is not clearly. Does the limitation of static graph cube is it cannot support range queries or it only can support latest data?
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors should improve their writing. Especially the punctuation makes the definitions hard to be understood.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors provide similarity of snapshots and two ratios in the Sec. 5. All of them are calculated based on the edges’ number. Why do you use similarity but not two ratios to proof the effectiveness?
\end{Comments}
\noindent \textbf{Response:} Actually we do use the two ratios to proof the effectiveness of the index. Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number. As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index. However, both theoretically and experimentally we find that the query efficiency and space cost of the index are both related to a metric named 'similarity of snapshots' in the manuscript, as shown in Table 6. If the value of similarity of snapshot. To sum up, we do use the two ratios to proof the effectiveness of the index, and similarity of snapshots is used to

### 2023-01-06 revision/response.tex

The point-to-point responses are given below.

\section{Response to Reviewer \#1}
\begin{Comments}
The expression of motivation is not clearly. Does the limitation of static graph cube is it cannot support range queries or it only can support latest data?
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors should improve their writing. Especially the punctuation makes the definitions hard to be understood.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors provide similarity of snapshots and two ratios in the Sec. 5. All of them are calculated based on the edges’ number. Why do you use similarity but not two ratios to proof the effectiveness?
\end{Comments}
\noindent \textbf{Response:} Actually we do use the two ratios to proof the effectiveness of the index. As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index. Similarity of snapshots is the metric which has a strong correlation with the two ratios, so it is used to measure the necessity of building index for a materialized view. In detail, both theoretically and experimentally we find that larger similarity of snapshots in a materialized view leads to higher acceleration ratio and lower space consumption ratio of the index. If the value of similarity of snapshots in a view is as low as $ 1 $, then there is no need to build index for the view and the baseline method to conduct queries is the best method, as we analyzed in Section 5.
%Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number. As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index. However, both theoretically and experimentally we find that the query efficiency and space cost of the index are both related to a metric named 'similarity of snapshots' in the manuscript, as shown in Table 6. If the value of similarity of snapshot. To sum up, we do use the two ratios to proof the effectiveness of the index, and similarity of snapshots is used to

### 2023-01-10 revision/response.tex

\begin{Comments}
In the experiments, authors should add an experiment of comparison with existing methods to evaluate the efficiency of their model.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The study of related works is insufficient, and some of the results and limitations of existing works are not discussed.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
The second parameter of MergeSnapshotExtre on Line 11, Algorithm 5 should be (u’, v’, t, a)?
\end{Comments}
\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $. In line 11 of Algorithm 5, the algorithm inserts $ e' $ into $ treeNode.snapshot $, which is equivalent to merge two snapshots: $ treeNode.snapshot $ and a temporary snapshot consisting of only $ e' $. However, edges in snapshot of each tree node are in form of $ (u,v,max,min) $, so we need to transform $ e' $ into $ (u',v',a,a) $, since $ a $ is both the maximum and minimum value of the numeric attribute in $ e' $. $ t $ is only used to determine whether the left child or the right child of $ treeNode $ should also be updated.

\section{Response to Reviewer \#2}
\setcounter{Comments}{0}
\begin{Comments}
D1: The management of snapshots should be described with more details. According to Def. 2, the snapshot is defined with a single timestamps. It looks like that when an edge forms at timestamp t, it never disappears. How do we maintain an edge with time range from t1 to t2? Otherwise, the limitation or applicability of the proposed method should be discussed.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
D2: Following D1, in current experimental datasets, DBLP and IMDB, all edges with single timestamps. I suggest adding experiments with datasets which contain edges with time ranges.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
D3: The effectiveness of partial materialization is not verified in experiments.
\end{Comments}
\noindent \textbf{Response:} test

\section{Response to Reviewer \#3}
\setcounter{Comments}{0}
\begin{Comments}
The experimental study only tests the proposed methods in this paper. I know the temporal graph cube is a novel problem studied in this paper, thus there is no existing algorithms/methods can direct handle it. However, is it possible to adapt some existing methods on graph summarizing, or static graph cube methods to handle the temporal graph cube problem as some baselines? Through comparing with modified existing methods can better show the advantages of the proposed methods.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
 some minor language issues should be addressed. E.g., In line 52, left column, page 2. "a index" $ \rightarrow $ "an index"
\end{Comments}
\noindent \textbf{Response:} Thank you very much for pointing out the negligence. We have corrected this error.

### 2023-01-20 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-10
response 1-20

\section{Temporal Graph Cube} \label{sec:temp_graph_cube}
%\subsection{Notations and Basic Concepts} \label{subsec:notation}
%\vspace*{-0.1cm}
%\subsection{Definitions}\label{subsec:definitions}
\begin{definition}[Temporal Multidimensional Network]
	\label{def:temp_multi_network}
	Let $\Gr=(\Vr, \Er, A, W)$ be an undirected temporal multidimensional network where $\Vr$ and $\Er$ are the set of nodes and edges respectively. Edges in $\Er$ are in the form of $(u, v, t, a)$, where $u$, $v$ are nodes in $\Vr$ and $t, a$ are timestamp and numeric attribute respectively attached to edges. $A=\{A_1, A_2, ... , A_n\}$ represents the dimensions of the network, or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ... , A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the $i$-th attribute. $ W(u) $ is the numeric value of $u$.
\end{definition}

@@

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item $\Vr' \subseteq \Vr$ and $\forall [v]$, an equivalence class in $\Vr$, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$, $\exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$. The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.

>>>>

\section{Temporal Graph Cube} \label{sec:temp_graph_cube}
%\subsection{Notations and Basic Concepts} \label{subsec:notation}
%\vspace*{-0.1cm}
%\subsection{Definitions}\label{subsec:definitions}
\begin{definition}[Temporal Multidimensional Network]
	\label{def:temp_multi_network}
	Let $\Gr=(\Vr, \Er, A, W)$ be an undirected temporal multidimensional network where $\Vr$ and $\Er$ are the set of nodes and edges respectively. Edges in $\Er$ are in the form of $(u, v, t, a)$. \revision{$ u $ and $ v $ are nodes in $\Vr$. $ t $ and $ a $ are timestamp and numeric attribute respectively attached to edges}. $A=\{A_1, A_2, ... , A_n\}$ represents the dimensions of the network or $n$ discrete attributes of nodes in $ \Vr $, i.e., $A(u)=\{A_1(u), A_2(u), ... , A_n(u)\}$ where $A_i(u)$ is the actual value of $u$ on the $i$-th attribute. $ W(u) $ is the numeric value of $u$.
\end{definition}

@@

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item $\Vr' \subseteq \Vr$ and $\forall [v]$, an equivalence class in $\Vr$, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$, $\exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$. The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$. For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$}
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.
